### 2023-04-03 paper-thesis/chapters/99-conclusion.tex
Finish Jesper's feedback

	\item \todo{irrelevance}
	\item Agda allows function arguments to be marked as erased, meaning that the value will be erased at runtime. An even stronger version of this feature is implementing a quantitive type system, such as in Idris~2~\cite{idris2}, which combines linear and dependent types. Implementing this in Spoofax should be possible, but it may be quite a bit of work as it is a complex type system.
	\item Agda has mixfix operators, which allows to define custom operators such as \verb|a and b|. This requires parsing to happen in multiple stages, where the first stage finds the mixfix operator definitions and the second stage parses expressions using them. This results in quite a complex parser, implementing these multiple stages in Spoofax using SDF3 is not possible without fundamental changes to the way that Spoofax works. One solution would be using an \emph{adaptive parsing algorithm}, which allows modification of the grammar during parsing. More research is needed to explore the possibilities of solving this problem.

@@

	\item Currently the language in the paper does not allow for recursive functions. Agda allows for functions that are structurally recursive, and uses termination checking to enforce this property. We see no reason why this couldn't be cleanly implemented in Statix, similar to the implementation of positivity checking in chapter~\ref{ch:datatypes}.

@@

\begin{itemize}
	\item There has not yet been an implementation of a sub-structural type system in Spoofax. A sub-structural type system is a type system that places restrictions on how often variables can be used. Now that languages with sub-structural type systems, such as Rust, are becoming popular, we should see if the goal of Statix to cover a broad range of type systems, still holds true for these. 
	\item Effect systems are a formal system that describe the side effects of a program. These allow programmers to specify what side effects a function has, which can then be verified by a type checker. Researching whether an effect system could be cleanly specified in Statix may lead to more insights on the limits of Statix.
	\item \todo{quantitive type system}
\end{itemize}

>>>>

	\item Agda allows for compile-time irrelevance annotations, which are a marker stating that the value of a certain variable is irrelevant, only that the type is non-empty matters~\cite[Irrelevance]{agda}. This can simplify some proofs, since all values of this type are considered equal. We see no reason why this couldn't be implemented in Statix.
	\item Agda allows function arguments to be marked as erased, meaning that the value will be erased at runtime. This is different than irrelevance annotations, as the value is still available at compile time. An even stronger version of this feature is implementing a quantitive type system, such as in Idris~2~\cite{idris2}, which combines linear and dependent types. Implementing this in Spoofax should be possible, but it may be quite a bit of work as it is a complex type system.
	\item Agda has mixfix operators, which allows to define custom operators such as \verb|a and b|~\cite[Mixfix Operators]{agda}. This requires parsing to happen in multiple stages, where the first stage finds the mixfix operator definitions and the second stage parses expressions using them~\cite{mixfix}. This results in quite a complex parser, implementing these multiple stages in Spoofax using SDF3 is not possible without fundamental changes to the way that Spoofax works. One solution would be using an \emph{adaptive parsing algorithm}, which allows modification of the grammar during parsing. More research is needed to explore the possibilities of solving this problem.

@@

	\item Currently the language in the paper does not allow for recursive functions. Agda allows for functions that are structurally recursive (as well as mutually structurally recursive), and uses termination checking to enforce this property. We see no reason why this couldn't be cleanly implemented in Statix, similar to the implementation of positivity checking in chapter~\ref{ch:datatypes}.

@@

\begin{itemize}
	\item There has not yet been an implementation of a sub-structural type system in Spoofax. A sub-structural type system is a type system that places restrictions on how often variables can be used. Now that languages with sub-structural type systems, such as Rust, are becoming popular, we should see if the goal of Statix to cover a broad range of type systems, still holds true for these. 
	\item Effect systems are a formal system that describe the side effects of a program. These allow programmers to specify what side effects a function has, which can then be verified by a type checker. Researching whether an effect system could be cleanly specified in Statix may lead to more insights on the limits of Statix.
	\item As mentioned above, implementing a quantitive type system, such as in Idris~2~\cite{idris2}, would be an interesting extension to this thesis. 
\end{itemize}
